AttCRISPR : a spacetime interpretable model for prediction of sgRNA on-target activity

### 2020-11-06 Paper/main.tex
11-6 paper

Clustered regularly interspaced short palindromic repeats (CRISPR) / CRIPSR associated protein 9 (Cas9) systems is preferred over other biological research and human medicine technologies now, 
beacuse of it's efficiency, robustness and programmability. 
Cas9 nucleases can be directed by short guide RNAs (sgRNAs) to introduce site-specific DNA double-stranded breaks in target, 
so to enable editing site-specific regions within the mammalian genome \citep{jinek2012a,cong2013multiplex,mali2013rnaguided}. 
CRISPR/Cas9, to a large extent, has developed genetic therapies at the cellular level, 
while there are still severe medical disadvantages even now which has greatly hindered the further clinical application of the CRISPR/Cas9 systems. 
One of these disadvantages is due to point mutations caused by off-target effect \citep{rubeis2018risks,kang2016introducing,ishii2017reproductive,liang2015crispr/cas9-mediated}. 
To overcome this disadvantage, a solution is to engineer CRISPR / Cas9 with higher specificities. 
That's why more and more higher specificities Cas9 variants, such as enhanced SpCas9 (eSpCas9(1.1)), 
Cas9-High Fidelity (SpCas9-HF1) \citep{ishii2017reproductive,slaymaker2016rationally}, hyper-accurate Cas9 (HypaCas9) \citep{kleinstiver2016high-fidelity}, 
been developed and bring a significant volume of experimental data, that is to say researchers have to face the difficulty of analyzing such huge and heterogeneous data.

@@

\begin{table}[!tpb]
    \processtable{Three sgRNA and their activity \label{Tab:optimum}} 
    {\begin{tabular}{@{}lll@{}}\toprule
        Index & sgRNA & Activity \\\midrule
        8493 & ACATGACTTTGGATTTCCCCAGG & 0.831\\
        8492 & ACATGACTTTGGATTCCCCCAGG & 0.869\\
        8491 & ACATGACTTTGGACTTCCCCAGG & 0.861\\
        \botrule
    \end{tabular}}\footnotesize\setlength{\parindent}{2em}{
\emph{Index} represents its index in the source data (Supplementary Data 1), 
\emph{Activity} represents its activity reported in WT-SpCas9 dataset. }
\end{table}
\begin{figure}[!tpb]
    \centerline{\includegraphics[width=86mm]{local0.eps}}
    \caption{
The scores of sgRNA with index of 8493 obtained by the temporal AttCRISPR. 
The bar plot reveals the score at each position at local level, while the line of dashes reveals the scores at global level. 
At global level we calculated the scores of all sgRNA, then average the scores at each position to obtain the global level which can be used as base line and is helpful to judge the relative height of the scores. 
}\label{fig:opt}
\end{figure}

>>>>

Clustered regularly interspaced short palindromic repeats (CRISPR) / CRIPSR associated protein 9 (Cas9) systems are preferred over other biological research and human medicine technologies now, 
beacuse of it's efficiency, robustness and programmability. 
Cas9 nucleases can be directed by short guide RNAs (sgRNAs) to introduce site-specific DNA double-stranded breaks in target, 
so to enable editing site-specific regions within genome \citep{jinek2012a,cong2013multiplex,mali2013rnaguided}. 
CRISPR/Cas9, to a large extent, has developed genetic therapies at the cellular level, 
while there are still severe medical disadvantages even now which has greatly hindered the further clinical application of the CRISPR/Cas9 systems. 
One of these disadvantages is due to unexpected insertion and deletion caused by off-target effect \citep{rubeis2018risks,kang2016introducing,ishii2017reproductive,liang2015crispr/cas9-mediated}. 
To overcome this disadvantage, a solution is to engineer CRISPR / Cas9 with higher specificities. 
That's why more and more higher specificities Cas9 variants, such as enhanced SpCas9 (eSpCas9(1.1)), 
Cas9-High Fidelity (SpCas9-HF1) \citep{ishii2017reproductive,slaymaker2016rationally}, hyper-accurate Cas9 (HypaCas9) \citep{kleinstiver2016high-fidelity}, 
been developed and bring a significant volume of experimental data, that is to say researchers have to face the difficulty of analyzing such huge and heterogeneous data.

@@

\begin{table}[!tpb]
    \processtable{Three sgRNA and their activity \label{Tab:optimum}} 
    {\begin{tabular}{@{}lll@{}}\toprule
        Index & sgRNA & Activity \\\midrule
        8493 & ACATGACTTTGGATTTCCCCAGG & 0.831\\
        8492 & ACATGACTTTGGATTCCCCCAGG & 0.869\\
        8491 & ACATGACTTTGGACTTCCCCAGG & 0.861\\
        \botrule
    \end{tabular}}\footnotesize\setlength{\parindent}{2em}{\emph{Note}: 
    \emph{Activity} of sgRNA represents the activity reported in WT-SpCas9 dataset (Supplementary Data 1). }
\end{table}
\begin{figure}[!tpb]
    \centerline{\includegraphics[width=86mm]{local0.eps}}
    \caption{
The scores of sgRNA with index of 8493 obtained by the temporal AttCRISPR. 
The bar plot reveals the score at each position at local level, while the line of dashes reveals the scores at global level. 
At global level we calculated the scores of all sgRNA, then average the scores at each position to obtain the global level which can be used as base line and is helpful to judge the relative height of the scores. 
}\label{fig:opt}
\end{figure}
